A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-25 tex/paper.tex
Seems like it's done

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``back-end" that generates a model spectrum.  In our adopted approach, the model 
spectrum for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library, 
\begin{equation} \label{eqn:interp}
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}),
\end{equation}
where we assign the symbol $\leadsto$ as an interpolation operator.  The
multi-dimensional interpolation in Eq.~\ref{eqn:interp} needs to be performed
many times, so computational efficiency is critical.  In practice, a simple
tri-linear interpolation is suitably fast, but introduces an undesirable level
of inaccuracy (particularly in the [Fe/H] dimension).  The interpolation
quality can be empirically estimated by performing the operation in
Eq.~\ref{eqn:interp} across a $\{\vt_{\ast}\}^{\rm grid}$ grid point, and then
comparing the interpolated spectrum with the corresponding library spectrum.
After an extensive exploration of such calculations \citep[see
also][]{husser12}, we concluded that this interpolation technique is found to
be accurate within a few percent per full-resolution model pixel and $\lesssim
1$\% once the spectrum is downsampled to the pixels of the detector. Ideally,
this pre-interpolation could be avoided if the spectral library was computed
over a refined grid (with a substantial up-front computational investment); but
for the time being, we can empirically propagate these interpolation
uncertainties into the likelihood calculations (as will be described in
Section~\ref{subsec:likelihood}).

@@

@@

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Kurucz}WASP-14 {\sc CfA/Kurucz} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6517 & 13 K \\
$\log_{10} g$ & \multicolumn{2}{c}{4.29 dex\tablenotemark{a}} \\
$\Z$ & -0.27 & 0.01 dex \\
$v \sin i$ & 4.29 & 0.05 $\kms$\\
$v_z$ & -4.62 & 0.02 $\kms$ \\
$\log_{10} \Omega$ & -12.7181 & 0.0004 \\
\cutinhead{Order 22 nuisance parameters}
$\log_{10} \cc{22}{0}$ &  0.0085 & 0.0005\\
$\cc{22}{1}$ & -0.014 & 0.002\\
$\cc{22}{2}$ & -0.014 & 0.002\\
$\cc{22}{3}$ & -0.003 & 0.001\\
\\
$b_{22}$ & 1.04 & 0.02 \\
$\log_{10} a_{{\rm g}, 22}$ & -14.63 & 0.02 $\log_{10}\left[ \textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1} \right ]$\\
$l_{22}$ & 7.5 & 0.8 $\kms$ \\

\cutinhead{Order 24 nuisance parameters}
$\log_{10} \cc{24}{0}$ & \multicolumn{2}{c}{0.00\tablenotemark{a}} \\
$\cc{24}{1}$ & -0.010 & 0.002 \\
$\cc{24}{2}$ & -0.011 & 0.001\\
$\cc{24}{3}$ &  0.000 & 0.001\\
\\
$b_{24}$ & 1.02 & 0.02 \\
$\log_{10} a_{{\rm g}, 24}$ & -14.61 & 0.02 $\log_{10}\left[\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}\right]$\\
$l_{24}$ & 7.3 & 0.6 $\kms$ \\
\enddata
\tablenotetext{a}{parameter value fixed}
\end{deluxetable}

\begin{figure}[!htb]
\begin{center}
\includegraphics{figs/metacomparison.pdf}
\caption{Comparing all the posteriors.}
\label{fig:metacomparison}
\end{center}
\end{figure}

@@

In addition to statistical and systematic error, one might expect that systematic instrumental error might also contribute to the parameter uncertainties. Commonly, one might estimate this error by fitting spectra taken by different instruments or at different times and then averaging the results. Additionally, one may add in an additional uncertainty ``floor'' that maps to the empirical scatter of typical spectroscopic fits. Such procedures generally make the assumption that this additional error contribution is Gaussian and independent in each parameter of interest. Our hierarchical Bayesian model avoids such a heuristic by
parameterizing the quality of fit self-consistently: because the parameter uncertainty is derived through the model itself, it preserves correlations between parameters, like the well known degeneracies between $T_{\rm eff}$, $\log g$, and $\Z$. Arbitrarily inflating the posterior estimates to reflect intuition would artificially destroy any natural degeneracy of parameters. However, for well-calibrated data sets from the same instrument any ill-effects are generally small. To quantify this error contribution for the WASP-14 spectrum in the traditional manner, we independently fit 4 separate \emph{TRES} spectra, and find a minimal scatter of $\sim10$ K and $\lesssim 0.001$ dex in $\Z$. When fitting these 4 spectra simultaneously in a hierarchical manner, we find that \todo{numbers}.

\comm{Finally, you can transition into the model systematics issue.  Here you want to do the 
modeling for Phoenix in orders 22-24 and demonstrate that you get much different parameters.  You 
will have to show the results, and then can take that opportunity to discuss the local covariance 
kernels.  Just show the results and make these two points, don't belabor the details: I don't 
know what to make of the weird Phoenix parameters.}

\begin{figure}[!htb]
\begin{center}
  \includegraphics[draft, width=0.5\textwidth,height=2in]{figs/PHOENIX_triangle.pdf}
\caption{ {\sc Phoenix} WASP-14 marginal posteriors.}
\label{fig:PHOENIX_posterior}
\end{center}
\end{figure}

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/residuals_PHOENIX_logg.pdf}
\caption{ {\sc Phoenix} WASP-14 model and residuals.}
\label{fig:residuals_PHOENIX}
\end{center}
\end{figure*}

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:PHOENIX}WASP-14 {\sc Phoenix} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6516.8 & 12.6 K \\
$\log_{10} g$ & \multicolumn{2}{c}{4.29 dex} \\
$\Z$ & -0.27 & 0.01 dex \\
$v \sin i$ & 4.29 & 0.05 $\kms$\\
$v_z$ & -4.62 & 0.02 $\kms$ \\
$\log_{10} \Omega$ & -12.72 & 0.0004 \\
\cutinhead{Order 22 nuisance parameters}
$\cc{22}{0}$ & & \\
$\cc{22}{1}$ & & \\
$\cc{22}{2}$ & & \\
$\cc{22}{3}$ & & \\
$b_{22}$ & & \\
$a_{{\rm g}, 22}$ & & \\
$l_{22}$ & & \\
\cutinhead{Order 23 nuisance parameters}
$\cc{23}{0}$ & & \\
$\cc{23}{1}$ & & \\
$\cc{23}{2}$ & & \\
$\cc{23}{3}$ & & \\
$b_{23}$ & & \\
$a_{{\rm g}, 23}$ & & \\
$l_{23}$ & & \\
\cutinhead{Order 24 nuisance parameters}
$\cc{24}{0}$ & & \\
$\cc{24}{1}$ & & \\
$\cc{24}{2}$ & & \\
$\cc{24}{3}$ & & \\
$b_{24}$ & & \\
$a_{{\rm g}, 24}$ & & \\
$l_{24}$ & & \\
\enddata
\end{deluxetable}

@@

While the CfA grid spectra fit well with no obvious features in the residual spectrum, because the PHOENIX spectrum is computed over a very broad spectral range with no specific tuning for solar type stars, there are likely to be a small amount of  ``outlier'' lines that appear in the residual spectrum (e.g., \citealt{husser13}, Figure 8). Some routines choose to ``sigma-clip'' the outlier lines and procede with fitting, however with such an approach it is difficult to quantify the effect that clipping a given line has on the final parameter estimates \citep{hogg10}. For example, what if a series of lines with $\sim$3 sigma disagreement actually has substantial discriminatory power against the stellar parameters?

This behaviour motivates the global and local kernels in a more sophisticated likelihood function, which includes a mechanism to account for the systematic mismatch of data spectrum and model spectrum.  The amplitude and scale of the global covariance grows to capture the discrepancy between data spectrum and synthetic spectrum. Including this global covariance broadens the posteriors on the stellar parameters, providing cushion against the outlier lines.

Using the {\sc Phoenix} models on WASP-14, we infer substantially different posteriors than with using the {\sc CfA/Kurucz} library. Figure~\ref{fig:PHOENIX_posterior} displays some of the relevant marginal posteriors, and Table~\ref{table:PHOENIX} compiles the estimates of the peaks of the posterior distribution and associated confidence intervals. Figure~\ref{fig:residuals_PHOENIX} demonstrates the quality of this approach and the structure of the associated residuals. Compared to the Kurucz residuals in Figure~\ref{fig:residuals_Kurucz}, there are two significant differences. First, the amplitude of the global covariance structure is larger. The global covariance acts as a way to parameterize the goodness or badness of a fit: better spectral models will have a lower covariance. Second, local covariance kernels track outlier spectral lines. These kernels can map out the regions of the spectrum which are outliers. The covariance hyperparameters provide a framework to identify these regions iteratively and in a self-consistent manner. The locations and amplitudes of these kernels output from the code would be useful information to consider when refining the models of stellar sythenis.

Comparing the results in Tables~\ref{table:Kurucz}~\&~\ref{table:PHOENIX} reveals that there is a systematic offset depending on which spectral library is used as a backend. Depending on the choice of spectral library, there may be systematic differences of 200 K or more in $T_{\rm eff}$ and 0.2 dex or more in $\Z$.

@@

Modeling late-type stellar atmosphere structures and their spectra is considerably more complex 
than for Sun-like stars, due to lingering uncertainties in the atmosphere physics and molecular 
opacities, as well as the presence of complex condensates (clouds) at the coolest temperatures.  
\comm{should probably add some citations to that statement.  Make a comment recognizing that 
various approaches have been taken, in context of Mann.}  \citet{rojas-ayala12} used a $K$-band 
spectrum at similar resolution to the SPEX data to estimate the key Gl~51 stellar parameters based 
on a line index technique.  They measured equivalent widths for the 2.205\,$\mu$m \ion{Na}{1} 
doublet and 2.263\,$\mu$m \ion{Ca}{1} triplet, along with a pseudo-continuum index defined over 
three narrow passbands, 2.070--2.090, 2.235--2.255, and 2.360--2.380\,$\mu$m (see their Figure 2 
for a useful visualization), designed to probe the spectral curvature induced by H$_2$O absorption 
bands.  With reference to a custom grid of {\sc BT-Settl} spectra\footnote{From the web simulator at \url{http://phoenix.ens-lyon.fr/simulator/index.faces}}, \citet{rojas-ayala12} find that 
these indices are consistent with $T_{\rm eff} = 3039\pm56$\,K and $[{\rm Fe/H}] = 0.28\pm0.17$.

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Gl51}Gl51 {\sc Phoenix} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 2998  & 17 K \\
$\log_{10} g$ & \multicolumn{2}{c}{5.0 dex} \\
$\Z$ & -0.01 & 0.04 dex \\
$v \sin i$ & 5.68 & 4.15 $\kms$\\
$v_z$ & 12.1 & 1.3 $\kms$ \\
$\log_{10} \Omega$ & -19.628  & 0.003 \\
\cutinhead{Nuisance parameters}
$\log_{10} c_0$ & \multicolumn{2}{c}{0.0} \\
$c_1$ & -0.011 & 0.002 \\
$c_2$ & 0.005 & 0.002 \\
$c_3$ & -0.002 & 0.001 \\
$b$ & 1.56 & 0.14 \\
$\log_{10} a_{\rm g} $ & -15.76 &  0.04 \\
$l$ & 116 & 20 $\kms$ \\
\cutinhead{Local kernel parameters}
$\log_{10} a$ & -14.75 & 0.18 \\
$\mu$ & 22055.9 & 0.8 \AA\\
$\sigma$ & 122 & 16 $\kms$ \\
\hline\\
$\log_{10}a$ & -14.83 & 0.19 \\
$\mu$ & 22083.1 & 0.9 \AA\\
$\sigma$ & 120 & 17 $\kms$  \\
\hline\\
$\log_{10}a$ & -14.81 & 0.27 \\
$\mu$ & 22609.2 & 1.3 \AA\\
$\sigma$ & 85 & 26 $\kms$  \\
\hline\\
$\log_{10}a$ & -14.73 & 0.24 \\
$\mu$ & 22625.2 & 1.1 \AA\\
$\sigma$ & 94 & 24 $\kms$ \\
\hline\\
$\log_{10}a$ & -14.74 & 0.20 \\
$\mu$ & 22652.2 & 0.8 \AA\\
$\sigma$ & 99 & 19 $\kms$ \\
\hline\\
$\log_{10}a$ & -14.81 & 0.31 \\
$\mu$ & 23380.1 & 1.0 \AA\\
$\sigma$ & 73 & 27 $\kms$ \\
\enddata
\end{deluxetable}

\comm{Now, present your results in a format that parallels the WASP-14 subsection.  You need a new 
Table and a sequence of figures; introduce them all here.}

\comm{Commentary on the necessity and utility of local covariance kernels here, with discussion of why Na and Ca lines are a pain.  It is also worth commenting on the potential for flexibly extending the shape of 
the kernel to mimic molecular bandheads, if one wanted to try and fit say the TiO bands.}

They note that the BT-Settl models manage to fit the overall spectral shape well, but consistently under-predict the strength of the \ion{Na}{1} and \ion{Ca}{1} lines, even when using the highest metallicity models. \citet{rajpurohit10} speculate that this discrepancy may result from inaccuracies in the oscillator strengths and opacities for the \ion{Na}{1} and \ion{Ca}{1} lines. When modelling the same region of spectrum as \citet{rojas-ayala12} (2.070--2.380$\mu$m) using an updated set of PHOENIX models \citep{husser13}, we find that \todo{report parameters}.

\begin{figure}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/Gl51_triangle.pdf}
  \caption{Gl51 stellar posterior.}
\label{fig:gl_posterior}
\end{center}
\end{figure}

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{figs/residuals_Gl51_logg.pdf}
  \caption{The Gl51 spectrum and residuals and many random draws from the final covariance matrix showing how the uncertainty in the ``outlier'' lines is identified by the local covariance kernels.}
\label{fig:regions}
\end{center}
\end{figure*}

\comm{A simple two-sentence (or so) wrap up on the future promise of this approach for late-type 
stars and their complex spectra.}

Complicated molecular structure is poorly known from models.

\clearpage

>>>>

We opt for the computationally expedient approach that employs a library of
model spectra, $\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm
eff}, \,\, \log{g}, \,\, [{\rm Fe/H}]]$.  However, it is worth noting that the
techniques developed here are applicable to {\it any} ``back-end" that
generates a model spectrum.  In our adopted approach, the model spectrum for an
arbitrary $\vt_{\ast}$ is interpolated from a spectral library,
\begin{equation} \label{eqn:interp} \flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto
\flam(\vt_{\ast}), \end{equation} where we assign the symbol $\leadsto$ as an
interpolation operator.  The multi-dimensional interpolation in
Eq.~\ref{eqn:interp} needs to be performed many times, so computational
efficiency is critical.  In practice, a simple tri-linear interpolation is
suitably fast, but introduces an undesirable level of inaccuracy
(particularly in the [Fe/H] dimension).  The interpolation quality can be
empirically estimated by performing the operation in Eq.~\ref{eqn:interp}
across a $\{\vt_{\ast}\}^{\rm grid}$ grid point, and then comparing the
interpolated spectrum with the corresponding library spectrum. After an
extensive exploration of such calculations \citep[see also][]{husser12}, we
concluded that the best combination of speed and accuracy can be achieved by
pre-computing a {\it refined} spectral library using a cubic spline
interpolation with a $\{\vt_{\ast}\}^{\rm grid}$ spacing of [20\,K, 0.1\,dex,
0.1\,dex], and then performing tri-linear interpolation over that refined
grid.  Overall, this interpolation technique is found to be accurate within
a few percent per full-resolution model pixel and $\lesssim 1$\% once the
spectrum is downsampled to the pixels of the detector.  Ideally, this
pre-interpolation could be avoided if the spectral library was computed
over a refined grid (with a substantial up-front computational investment);
but for the time being, we can empirically propagate these interpolation
uncertainties into the likelihood calculations (as will be described in
Section~\ref{subsec:likelihood}).

@@

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Kurucz}WASP-14 {\sc CfA/Kurucz} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6517 & 13 K \\
$\log_{10} g$\tablenotemark{a} & \multicolumn{2}{c}{4.29 dex} \\
$\Z$ & -0.27 & 0.01 dex \\
$v \sin i$ & 4.29 & 0.05 $\kms$\\
$v_z$ & -4.62 & 0.02 $\kms$ \\
$\log_{10} \Omega$\tablenotemark{b} & -12.7181 & 0.0004\\
\cutinhead{Order 22 nuisance parameters}
$\log_{10} \cc{22}{0}$ &  0.0085 & 0.0005\\
$\cc{22}{1}$ & -0.014 & 0.002\\
$\cc{22}{2}$ & -0.014 & 0.002\\
$\cc{22}{3}$ & -0.003 & 0.001\\
\\
$b_{22}$ & 1.04 & 0.02 \\
$\log_{10} a_{{\rm g}, 22}$ & -14.63 & 0.02 $\log_{10}\left[ \textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1} \right ]$\\
$l_{22}$ & 7.5 & 0.8 $\kms$ \\

\cutinhead{Order 24 nuisance parameters}
$\log_{10} \cc{24}{0}$\tablenotemark{a} & \multicolumn{2}{c}{0.00} \\
$\cc{24}{1}$ & -0.010 & 0.002 \\
$\cc{24}{2}$ & -0.011 & 0.001\\
$\cc{24}{3}$ &  0.000 & 0.001\\
\\
$b_{24}$ & 1.02 & 0.02 \\
$\log_{10} a_{{\rm g}, 24}$ & -14.61 & 0.02 $\log_{10}\left[\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}\right]$\\
$l_{24}$ & 7.3 & 0.6 $\kms$ \\
\enddata
\tablenotetext{a}{parameter value fixed}
\tablenotetext{b}{The {\sc CfA/Kurucz} library is scaled such that the average flux is unity, rather than given in units of flux at the stellar surface, so this value is an unknown multiple of $R^2/d^2$.}
\end{deluxetable}

@@

\begin{figure}[!htb]
\begin{center}
\includegraphics{figs/metacomparison.pdf}
\caption{The posterior peaks and widths for various determination of the stellar parameters of WASP-14. The determinations in \citet{torres12} are shown along with the estimates using the {\sc CfA/Kurucz} synthetic library and the {\sc PHOENIX} synthetic library. \todo{What else do we want to show on here?}}
\label{fig:metacomparison}
\end{center}
\end{figure}

@@

In addition to statistical and systematic error, one might expect that systematic instrumental error might also contribute to the parameter uncertainties. Commonly, one might estimate this error by fitting spectra taken by different instruments or at different times and then averaging the results. Additionally, one may add in an additional uncertainty ``floor'' that maps to the empirical scatter of typical spectroscopic fits. Such procedures generally make the assumption that this additional error contribution is Gaussian and independent in each parameter of interest. Our hierarchical Bayesian model avoids such a heuristic by
parameterizing the quality of fit self-consistently: because the parameter uncertainty is derived through the model itself, it preserves correlations between parameters, like the well known degeneracies between $T_{\rm eff}$, $\log g$, and $\Z$. Arbitrarily inflating the posterior estimates to reflect intuition would artificially destroy any natural degeneracy of parameters. However, for well-calibrated data sets from the same instrument any ill-effects are generally small. To quantify this error contribution for the WASP-14 spectrum in the traditional manner, we independently fit 4 separate \emph{TRES} spectra, and find a minimal scatter of $\sim20$ K and $\lesssim 0.02$ dex in $\Z$. When fitting these 4 spectra simultaneously in a hierarchical manner, we find that \todo{numbers}.

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:PHOENIX}WASP-14 {\sc Phoenix} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6273 & 15 K \\
$\log_{10} g$\tablenotemark{a} & \multicolumn{2}{c}{4.29 dex} \\
$\Z$ & -0.498 & 0.006 dex \\
$v \sin i$ & 4.89 & 0.05  $\kms$\\
$v_z$ & -4.86 & 0.02 $\kms$ \\
$\log_{10} \Omega$ & -19.678  & 0.001 \\
\cutinhead{Order 22 nuisance parameters}
$\cc{22}{0}$ & 0.012 & 0.001 \\
$\cc{22}{1}$ & -0.021 & 0.003 \\
$\cc{22}{2}$ & -0.018 & 0.002 \\
$\cc{22}{3}$ & -0.004 & 0.002 \\
$b_{22}$ & 1.02 & 0.02 \\
$\log_{10}a_{{\rm g}, 22}$ & -14.33 & 0.02 $\log_{10}\left[\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}\right]$\\
$l_{22}$ & 9.0 & 0.5 $\kms$\\
\cutinhead{Order 23 nuisance parameters}
$\cc{23}{0}$ & 0.004 & 0.001  \\
$\cc{23}{1}$ & -0.015 & 0.003 \\
$\cc{23}{2}$ & -0.024 & 0.003 \\
$\cc{23}{3}$ & -0.002 & 0.003 \\
$b_{23}$ & 1.00 & 0.02 \\
$\log_{10}a_{{\rm g}, 23}$ & -14.30 & 0.02 $\log_{10}\left[\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}\right]$\\
$l_{23}$ & 9.8 & 0.5 $\kms$\\
\cutinhead{Order 24 nuisance parameters}
$\cc{24}{0}$\tablenotemark{a} & \multicolumn{2}{c}{0.00} \\
$\cc{24}{1}$ & -0.009 & 0.003 \\
$\cc{24}{2}$ & -0.012 & 0.003 \\
$\cc{24}{3}$ & -0.001 & 0.002 \\
$b_{24}$ & 1.00 & 0.02 \\
$\log_{10} a_{{\rm g}, 24}$ & -14.32 & 0.02 $\log_{10}\left[\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}\right]$\\
$l_{24}$ & 8.5 & 0.5 $\kms$ \\
\enddata
\tablenotetext{a}{parameter value fixed}
\tablecomments{ \todo{There are literally 100 other parameters for the $\sim30$ local kernels. How should I present these in the Table?}}
\end{deluxetable}

\begin{figure}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/PHOENIX_triangle.pdf}
\caption{ {\sc Phoenix} WASP-14 marginal posteriors. Note $v \sin i$ may differ because the libraries assume different micro and macroturbulence.}
\label{fig:PHOENIX_posterior}
\end{center}
\end{figure}

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/residuals_PHOENIX_logg.pdf}
\caption{ {\sc Phoenix} WASP-14 model and residuals.}
\label{fig:PHOENIX_residuals}
\end{center}
\end{figure*}

@@

While the CfA grid spectra fit well with no obvious features in the residual spectrum, because the PHOENIX spectrum is computed over a very broad spectral range with no specific tuning for solar type stars, there are likely to be a small amount of  ``outlier'' lines that appear in the residual spectrum (e.g., \citealt{husser13}, Figure 8). Some routines choose to ``sigma-clip'' the outlier lines and procede with fitting, however with such an approach it is difficult to quantify the effect that clipping a given line has on the final parameter estimates \citep{hogg10}. For example, if a series of lines with $\sim$3 sigma disagreement actually has substantial discriminatory power against the stellar parameters, then this information would be lost in a sigma-clipping procedure.

This behavior of the {\sc PHOENIX} library motivates the use of global and local covariance kernels in a sophisticated likelihood function. The amplitude and scale of the global covariance grows to capture the discrepancy between data spectrum and synthetic spectrum, and acts as a mechanism to account for the systematic mismatch of data spectrum and model spectrum. Including this covariance broadens the posteriors on the stellar parameters, while the local covariance kernels provide cushion against outlier lines.

Using the {\sc Phoenix} models on WASP-14, we infer substantially different posteriors than with the {\sc CfA/Kurucz} library. Figure~\ref{fig:PHOENIX_posterior} displays some of the relevant marginal posteriors, and Table~\ref{table:PHOENIX} compiles the estimates of the peaks of the posterior distribution and associated confidence intervals. Figure~\ref{fig:PHOENIX_residuals} demonstrates the quality of this approach and the structure of the associated residuals. Compared to the Kurucz residuals in Figure~\ref{fig:Kurucz_residuals}, there are two significant differences. First, the amplitude of the global covariance structure is larger. Because the amplitude of the covariance (both global and local) is an indirect parameterization of the quality of a model fit, better spectral models will have a lower covariance. Second, local covariance kernels are instantiated to track outlier spectral lines. These kernels map out the regions of the spectrum where there are large outlier spectral lines. The parameters of these local kernels provide a framework to identify incorrectly modelled spectral lines iteratively and in a self-consistent manner, and would be a useful data product to consider when refining the synthetic stellar models. The most striking difference between the two libraries is the $\sim$200 K systematic offset in temperature. Any systematic bias that results is most likely a direct consequence of the various physics and atomic constants included in each synthetic library.

@@

Modeling late-type stellar atmosphere structures and their spectra is
considerably more complex than for Sun-like stars, due to lingering
uncertainties in the atmosphere physics and molecular opacities, as well as the
presence of complex condensates (clouds) at the coolest temperatures
\citep{allard13}, making it considerably more challenging to determine stellar
properties \citep{rajpurohit14}. Various approaches have been taken to
determine stellar parameters in the face of these difficulties, including
iteratively masking the regions with poor spectral agreement \citep{mann13}.
However, \citet{mann13} note that such a scheme may exclude slightly discrepant
regions of the spectrum that actually contain a significant amount of
information useful to discriminate stellar properties, and that a more
sophisticated approach would weight each spectral region based upon its
consistency with the data. \citet{rojas-ayala12} used a $K$-band spectrum at
similar resolution to the SPEX data to estimate the key Gl~51 stellar
parameters based on a line index technique.  They measured equivalent widths
for the 2.205\,$\mu$m \ion{Na}{1} doublet and 2.263\,$\mu$m \ion{Ca}{1}
triplet, along with a pseudo-continuum index defined over three narrow
passbands, 2.070--2.090, 2.235--2.255, and 2.360--2.380\,$\mu$m (see their
Figure 2 for a useful visualization), designed to probe the spectral curvature
induced by H$_2$O absorption bands.  With reference to a custom grid of {\sc
BT-Settl} spectra\footnote{Created using the web simulator at
   \url{http://phoenix.ens-lyon.fr/simulator/index.faces}},
\citet{rojas-ayala12} find that these indices are consistent with $T_{\rm
eff} = 3039\pm56$\,K and $[{\rm Fe/H}] = 0.28\pm0.17$.

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Gl51}Gl51 {\sc Phoenix} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 2998  & 17 K \\
$\log_{10} g$\tablenotemark{a} & \multicolumn{2}{c}{5.0 dex} \\
$\Z$ & -0.01 & 0.04 dex \\
$v \sin i$ & 5.68 & 4.15 $\kms$\\
$v_z$ & 12.1 & 1.3 $\kms$ \\
$\log_{10} \Omega$ & -19.628  & 0.003 \\
\cutinhead{Nuisance parameters}
$\log_{10} c_0$\tablenotemark{a} & \multicolumn{2}{c}{0.0} \\
$c_1$ & -0.011 & 0.002 \\
$c_2$ & 0.005 & 0.002 \\
$c_3$ & -0.002 & 0.001 \\
$b$ & 1.56 & 0.14 \\
$\log_{10} a_{\rm g} $ & -15.76 &  0.04 \\
$l$ & 116 & 20 $\kms$ \\
\cutinhead{Local kernel parameters}
$\log_{10} a$ & -14.75 & 0.18 \\
$\mu$ & 22055.9 & 0.8 \AA\\
$\sigma$ & 122 & 16 $\kms$ \\
\hline\\
$\log_{10}a$ & -14.83 & 0.19 \\
$\mu$ & 22083.1 & 0.9 \AA\\
$\sigma$ & 120 & 17 $\kms$  \\
\hline\\
$\log_{10}a$ & -14.81 & 0.27 \\
$\mu$ & 22609.2 & 1.3 \AA\\
$\sigma$ & 85 & 26 $\kms$  \\
\hline\\
$\log_{10}a$ & -14.73 & 0.24 \\
$\mu$ & 22625.2 & 1.1 \AA\\
$\sigma$ & 94 & 24 $\kms$ \\
\hline\\
$\log_{10}a$ & -14.74 & 0.20 \\
$\mu$ & 22652.2 & 0.8 \AA\\
$\sigma$ & 99 & 19 $\kms$ \\
\hline\\
$\log_{10}a$ & -14.81 & 0.31 \\
$\mu$ & 23380.1 & 1.0 \AA\\
$\sigma$ & 73 & 27 $\kms$ \\
\enddata
\tablenotetext{a}{parameter value fixed}
\end{deluxetable}

Using the same region of the spectrum as \citet{rojas-ayala12} and the {\sc PHOENIX} library \citep{husser13}, and an appropriate $\delta$-function prior on $\log
g = 5.0$, we infer parameters that are consistent with the \citet{rojas-ayala}
approach: $T_{\rm eff} = 2998 \pm17$\,K, $[{\rm Fe/H}] = -0.01\pm0.04$\,dex, and
$v \sin i \lesssim 10$\,km s$^{-1}$.  Figure~\ref{fig:Gl51_posterior}
displays some relevant marginal projections of the posterior-space, and
Table~\ref{table:Gl51} compiles our estimates of the peaks of the marginal
posteriors and associated confidence intervals for all parameters employed in
the modeling.  Figure~\ref{fig:Gl51_residuals} demonstrates the overall
quality of this approach in reproducing the Gl51 spectrum and, most
significantly, the structure of the associated residuals.

\begin{figure}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/Gl51_triangle.pdf}
  \caption{Gl51 stellar posterior marginalized over the other nuisance parameters, including the local covariance kernels which account for the \ion{Na}{1} and \ion{Ca}{1} lines.}
\label{fig:Gl51_posterior}
\end{center}
\end{figure}

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{figs/residuals_Gl51_logg.pdf}
  \caption{The Gl51 spectrum and residuals and many random draws from the final covariance matrix showing how the uncertainty in the ``outlier'' lines is identified by the local covariance kernels.}
\label{fig:Gl51_residuals}
\end{center}
\end{figure*}

We find, like \citet{rojas-ayala12} do, that the {\sc PHOENIX} models manage to fit the overall spectral shape well, but consistently under-predict the strength of the \ion{Na}{1} and \ion{Ca}{1} lines, even when using high metallicity models. \citet{rajpurohit10} speculate that this discrepancy may result from inaccuracies in the oscillator strengths and opacities for the \ion{Na}{1} and \ion{Ca}{1} lines. Fortunately, the local kernels provide a mechanism for self-consistently determining the weights of discrepant spectral lines, like that speculated about by \citet{mann13}, such that they bring their full information content to bear on the stellar posterior distribution without bias. Figure~\ref{fig:Gl51_residuals} shows that these kernels have identified these two line groups as problematic and appropriately inflated the covariance for this region of spectrum, reducing the ability of these lines to bias the final stellar parameters.

In other regions of the spectrum, late type stars also present other types of spectral outliers. In particular, the TiO bandheads can produce a complicated saw-like residual pattern. Like a Gaussian function was used as the starting point for residuals produced by single spectral lines, the local kernel framework could be extended to include an additional kernel which would mimic the appearance of the residuals generated from poorly-modelled molecular bandheads. For example, the product of a truncated exponential and a \matern\ kernel or other similar hybrid kernels might capture this residual behavior well. Our forward modelling technique has great potential for fitting the spectra of late-type stars to derive stellar parameters. Because large regions of the spectrum may be in modest but not perfect agreement with the data, the usage of covariance kernels allows us to utilize these mildly discrepant regions by self-consistently determining their weighted contribution, maximizing the potential inference on the stellar parameters of interest.
